---
title       : Estimating Vehicle Fuel Economy
subtitle    : A tool for consumers & manufacturers 
author      : Jacob Schwan
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## What is it?

A web application that will:

1. Estimate a vehicle's combined miles per gallon (MPG) based on:
    * Model Year
    * Number of Cylinders
    * Drive Type (2 or 4 wheel)
    * Transmission Type
    * Engine Displacement
    * Presence of a Supercharger or Turbocharger

2. Provide a list of vehicles that match the provided specifications, if any 
exist.

Play with it at: http://blackbrass88.shinyapps.io/EstimatingMPG

---

## Who wants it?

### Consumers

* Consumers care about MPG when shopping for a car but don't know what 
specifications to look for to improve it.

* This tool lets them play with the specifications and see an estimate of the
resulting combined MPG

* Once they have the specifications they like, they can see if there are any
vehicles produced that match.

### Manufacturers

* Vehicle producers can use the tool to test out theoretical vehicle designs
and determine their estimated MPG.

* They will also see how much competition there is in the market for vehicles
with similar specifications

---

## How was it built?

* Raw data was obtained from the [FuelEconomy.gov](https://www.fueleconomy.gov/feg/ws/index.shtml)

* Data from 1987 to 2016 was used to limit empty or NA variables

* A generalized linear model was produced using the following code:
```{r, eval=FALSE}
require(caret); require(dplyr)
modelData <- select(fuelData, -make, -model)
inTrain <- createDataPartition(y=modelData$comb08,p=0.8,list=F)
training <- modelData[inTrain,]
testing <- modelData[-inTrain,]
modelGLM <- train(comb08 ~ .,data=training,method="glm")
```

* [Data Cleaning & Model Building Script Available on GitHub](
https://github.com/blackbrass88/DataProductsProject/blob/master/analysis.R)

---

## How was it built?

```{r}
modelGLM <- readRDS("../modelGLM.rds")
modelGLM
```
